Turbulence in compact to giant H~II regions

### 2022-12-09 strucfunc_paper.tex
Finish discussion of power law slope

@@

\newcommand\ha{\ensuremath{\text{H}\alpha}}
\newcommand\Wav[1]{\ensuremath{\lambda #1}}
% Chemical formulae
\newcommand*\chem[1]{\ensuremath{\mathrm{#1}}}
\newcommand\csound{\ensuremath{c_{\text{s}}}}
\newcommand\FNa{\textsuperscript{a}}

@@

We use the velocity field presented in \citet{1987A&A...176..347H} to analyze the Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}.
The EON is an extended region in southwest direction from the Huygens region which presents a diminution in the brightness.
The observational data was obtained using a Fabry-Pérot interferometer with a étalon separation of 0.5 mm on the 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\theta^{1}\)Ori C.

@@

\newcommand\DDD{\ensuremath{_{\mathrm{3D}}}}
For incompressible Kolmogorov turbulence,
the predicted slope of the three-dimensional structure function is \(m\DDD = 2/3\),
but intermittency and compressibility \citep{Schmidt:2008a}
can increase this to \(m\DDD \approx 0.8\) in the subsonic regime,
and up to \(m\DDD = 1\) in the supersonic regime.
Comparison with our measurements is complicated by projection smoothing,
which mean that \(m\DDD\) is only
observed directly for separations larger than the line-of-sight depth
of the emitting regions.
For smaller separations, one potentially observes a steeper slope:
\(m = m\DDD + 1 + \delta\kappa\),
where \(\delta\kappa\) represents the effects of emissivity fluctuations
along the line of sight \citep{Brunt:2004a},
and varies from \(\delta\kappa = 0\) in the incompressible limit
to \(\delta\kappa = -1\) in the case of strongly driven supersonic turbulence.

It is therefore not surprising that we see no significant correlation
between \(m\) and \(\sigma^2\pos\) 
(\(p = 0.33\), Table~\ref{tab:RestStats}).
Although theoretically one might expect a positive correlation of \(m\DDD\)
with the amplitude of the velocity fluctuations
due to the transition from subsonic
to supersonic turbulence \citep{Galtier:2011a},
this will be offset by a decrease in \(\delta\kappa\) 
if the amplitude of the density fluctuations
(and hence emissivity fluctuations) increases along
with the velocity fluctuations.

In figure

We also find no clear evidence for a broken power-law in any of our
structure functions, as has been suggested in previous studies.
Although in some regions we do observe a steepening at the smallest scales
(for example Figures~\ref{fig:strucfunc-fit-Galactic}a, \ref{fig:strucfunc-fit-MC}ab),
this can be accounted for in our model fits by
the spatial smoothing caused by atmospheric seeing.
This has a noticeable effect on the structure function at scales of
up to 5 times the FWHM of the seeing (Appendix~\ref{sec:effects-seeing-struc}).
There is a hint in the highest quality datasets that there may also be
a real steepening of the structure function at small scales
(see section~\ref{sec:sanity-check-derived}),
but higher spatial resolution observations are required in order to study this.

Theoretically, one might expect a positive correlation of the slope with the
amplitude of the velocity fluctuations, due to the transition from subsonic
to supersonic turbulence \citep{Galtier:2011a}.
However, the predicted change of slope is rather small,
\(\delta m \approx 0.2\)
\citep{Federrath:2021r},
and only one of our sources (30~Dor) is clearly in the supersonic regime,
so it is perhaps not surprising that we do not find a significant correlation
(\(p = 0.33\), Table~\ref{tab:RestStats}).
This is further complicated by the effect of projection along the line of sight

Theoretically, one might expect

@@

\begin{figure}
\centering 
\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
\caption{
  Panels a--g show histograms (blue) of the probability density function (PDF)
  of the \ha{} surface brightness of \hii{} regions in our sample.
  Smooth lines (orange) show fitted log-normal distributions.
  In order to suppress fluctuations on scales
  smaller than the correlation length,
  Surface brightness maps were rebinned by averaging
  into pixels of size \(0.5 r_0\) before calculating the PDF.
  In panel~h is plotted for each source of the previous panels
  the ratio of velocity dispersions
  (see Figure~\ref{fig:los-vs-pos})
  as a function of the
  RMS fractional brightness fluctuations calculated from the PDFs.
}
\label{fig:brightness-pdfs}
\end{figure}

@@

The relationship \(\text{L}_{\text{H}} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
\citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).
Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).

There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\text{H}_{\alpha})\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.

@@

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\theta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of  \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} or \SI{e37.18}{erg.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

%Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
%In this case we merge the first three points of the structure function.
%A detailed description of the model fit is given in
%section~\ref{sec:example-results-orion} and will
%not be repeated here.
At the largest scales, which are not used in the model fitting,
one sees a downturn in the structure function from
\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
\SI{7}{km^{2}.s^{-2}} at \(r  \SI{0.5}{pc}\).
%This is similar to the behavior expected for tapered fluctuations
%(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
%in which the velocity dispersion is higher in the center of the map
%than in the periphery.

@@

%The seeing width is much smaller than the angular scale of the observations
\subsubsection{Comparison with previous studies}
\label{sec:comparison-orion}

@@

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
%It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
%The velocity field shows several expanding shells, related to the stellar population, and the massive %protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
%A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
%The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
%In this case we merge the first two points.
%The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
Using the \ha{} luminosity as a diagnostic of the ionizing flux \(Q_0\) \citet{2007MNRAS.379.1279S} measured a value of \SI{e50.47}{photons.s^{-1}}.
%Young clusters like Trumpler 14 and 16, and Collinder 228 form the Car OB1 association, one of the largest OB associations on the Galaxy.
%This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars.
The most luminous star is the blue variable $\eta$ Car.
%As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
%This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.

@@

(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
%For this region we merge the first two points of the structure function.
%As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
%NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
This is the first time turbulence is characterized in 30~Doradus using the structure function.

>>>>

\usepackage{upgreek}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newcommand\ha{\ensuremath{\text{H}\upalpha}}
\newcommand\hb{\ensuremath{\text{H}\upbeta}}
\newcommand\Wav[1]{\ensuremath{\lambda #1}}
% Chemical formulae
\newcommand*\chem[1]{\ensuremath{\mathrm{#1}}}
\newcommand\csound{\ensuremath{c_{\text{s}}}}
\newcommand\FNa{\textsuperscript{a}}
\newcommand\Mach{\ensuremath{\mathcal{M}}}

@@

We use the velocity field presented in \citet{1987A&A...176..347H} to analyze the Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}.
The EON is an extended region in southwest direction from the Huygens region which presents a diminution in the brightness.
The observational data was obtained using a Fabry-Pérot interferometer with a étalon separation of 0.5 mm on the 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\uptheta^{1}\)Ori C.

@@

\newcommand\DDD{\ensuremath{_{\mathrm{3D}}}}
For incompressible Kolmogorov turbulence,
the predicted slope of the three-dimensional structure function is \(m\DDD = 2/3\),
but intermittency and compressibility \citep{Schmidt:2008a}
can increase this to \(m\DDD \approx 0.8\) in the subsonic regime,
and up to \(m\DDD = 1\) in the supersonic regime.
Comparison with our measurements is complicated by projection smoothing
\citep{1984ApJ...277..556S},
which implies that \(m\DDD\) is only
observed directly for separations larger than the line-of-sight depth
of the emitting regions.
For smaller separations, one potentially observes a steeper slope:
\(m = m\DDD + 1 + \delta\kappa\),
where \(\delta\kappa\) represents the effects of emissivity fluctuations\footnote{%
  Note that literature on turbulence in molecular clouds discuss fluctuations of \emph{density}
  since they are mainly concerned with emission lines
  whose emissivity is approximately linearly proportional to density.
  In the case of photoionized regions, the emissivity of important lines such as \ha{}
  is proportional to \emph{density-squared},
  so in adopting the results of \citet{Brunt:2004a} we substitute emission measure
  (or its proxy, \ha{} surface brightness)
  in place of column density. 
}
along the line of sight \citep{Brunt:2004a},
and varies from \(\delta\kappa = 0\) in the incompressible limit
to \(\delta\kappa = -1\) in the case of strongly driven supersonic turbulence.
In this latter case, the effects of projection smoothing and emissivity fluctuations
cancel out, leading once more to \(m \approx m\DDD\).

The \hii{} regions of our sample span the transonic regime,
from subsonic velocity fluctuations in the Galactic sources
to supersonic fluctuations in the more luminous extragalactic sources. 
It is therefore not surprising that we see no significant correlation
between \(m\) and \(\sigma^2\pos\) 
(\(p = 0.33\), Table~\ref{tab:RestStats}).
Although theoretically one might expect a positive correlation of \(m\DDD\)
with the amplitude of the velocity fluctuations
due to the transition from subsonic
to supersonic turbulence \citep{Galtier:2011a},
this will be offset by a decrease in \(\delta\kappa\) 
if the amplitude of the density fluctuations
(and hence emissivity fluctuations) increases along
with the velocity fluctuations.

Evidence for just such an increase is shown in Figure~\ref{fig:brightness-pdfs}g,
which shows how the fractional width of the probability distribution of
large-scale \ha{} surface brightness fluctuations
varies with the RMS turbulent Mach number, \Mach{},
of the three-dimensional velocity fluctuations.
The Mach number is estimated by assuming that the plane-of-sky velocity dispersion is
a good estimate of the turbulent fluctuations in one dimension
and that the turbulence is isotropic, yielding:
\(\Mach = \sqrt{3} \sigma\pos / \csound\),
where an ionized sound speed of \(\csound = \SI{11}{km.s^{-1}}\)
is assumed for all sources.
\newcommand\longsig[1]{\ensuremath{\langle \delta #1^2 \rangle^{1/2} / #1_0}}
\newcommand\shortsig[1]{\ensuremath{\sigma_{#1/#1_0}}}
The RMS fractional width of density fluctuations in a turbulent medium,
\(\shortsig{\rho} \equiv \longsig{\rho}\),
is predicted to depend linearly on the Mach number as
\(\shortsig{\rho} = b \Mach\),
where \(b\) depends on the nature of the turbulent driving \citep{Federrath:2010z},
varying between \(b = 1/3\) for solenoidal driving and \(b = 1\) for compressive driving.
This is shown by gray shading\footnote{%
  In the figure, it is assumed that the relative fluctuations in surface brightness
  and density are equal, which is a result of the
  cancellation between two effects. First, that the volumetric \ha{} emissivity \(E\)
  is proportional to density squared, so that \(\shortsig{E} = 2 \shortsig{\rho}\). 
  Second, that fluctuations in surface brightness \(S\) are related to those in emissivity
  by \(\shortsig{S} = R^{1/2} \shortsig{E}\), where \(R\)
  is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
  For an emissivity power spectrum \(P(k) \sim k^{-3}\)
  and assuming a ratio of map size to correlation length
  of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
  we find \(R \approx 0.2\) and hence \(\shortsig{S} \approx \shortsig{\rho}\). 
}
in Figure~\ref{fig:brightness-pdfs}h,
where it can be seen that many of the sources with subsonic velocity dispersions
(\(\Mach < 1\)) fall to the right of the theoretical prediction,
implying that other factors in addition to turbulence are responsible for
producing the fluctuations in density and surface brightness in these regions
(see also section 4.5 of \citealp{arthur2016turbulence}).
For our highest luminosity source of 30~Dor on the other hand,
the velocity dispersion is clearly supersonic (\(\Mach \approx 2.7\))
and, although the surface brightness fluctuations are also larger than in the other sources,
they are consistent with being caused by turbulence-induced density fluctuations.

We find no clear evidence for a broken power-law in any of our
structure functions, as has been claimed in previous studies.
Although in some regions we do observe a steepening at the smallest scales
(for example Figures~\ref{fig:strucfunc-fit-Galactic}a, \ref{fig:strucfunc-fit-MC}ab),
this can be accounted for in our model fits by
the spatial smoothing caused by atmospheric seeing.
This has a noticeable effect on the structure function at scales of
up to 5 times the FWHM of the seeing (Appendix~\ref{sec:effects-seeing-struc}).
There is a hint in the highest quality datasets that there may also be
a real steepening of the structure function at small scales
(see section~\ref{sec:sanity-check-derived}),
but higher spatial resolution observations are required in order to study this.

% Theoretically, one might expect a positive correlation of the slope with the
% amplitude of the velocity fluctuations, due to the transition from subsonic
% to supersonic turbulence \citep{Galtier:2011a}.
% However, the predicted change of slope is rather small,
% \(\delta m \approx 0.2\)
% \citep{Federrath:2021r},
% and only one of our sources (30~Dor) is clearly in the supersonic regime,
% so it is perhaps not surprising that we do not find a significant correlation
% (\(p = 0.33\), Table~\ref{tab:RestStats}).
% This is further complicated by the effect of projection along the line of sight

@@

\begin{figure}
\centering 
\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
\caption{
  Panels a--g show histograms (blue) of the probability density function (PDF)
  of the \ha{} surface brightness of \hii{} regions in our sample.
  Smooth lines (orange) show fitted log-normal distributions.
  In order to suppress fluctuations on scales
  smaller than the correlation length,
  surface brightness maps were rebinned by averaging
  into pixels of size \(0.5 r_0\) before calculating the PDF.
  Also shown are the RMS Mach number of three-dimensional
  velocity fluctuations (panel~h)
  and the ratio of plane-of-sky to line-of-sight velocity dispersions (panel~i),
  each plotted as a function of the
  RMS fractional brightness fluctuations calculated from the PDFs.
}
\label{fig:brightness-pdfs}
\end{figure}

@@

The relationship \(\text{L}_{\ha} \propto \sigma^{\alpha}\) has been extensively investigated  in the context of giants \hii{} regions obtaining a value for \(\alpha\) of \( \sim 4\)\citep{terlevich1981,1988A&A...201..199A} and \num{2.87 \pm 0.2} \citep{Rozas:2006b}.
Complementing previous results \citet{2012MNRAS.422.3339W} found that star-forming regions at \(z \sim 1.3\) and local \hii{} regions follow a relation with \(\alpha = 4.18 \pm 0.21\).
\citet{Moiseev:2015a} found that this relation also holds for dwarf galaxies with a value of \(\alpha \sim 5\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated \hb{} line luminosity for new data of 36 giant \hii{} regions obtaining \(\text{L}_{\hb} \propto \sigma^{5.02 \pm 0.21}\).
Recently, \citet{2020ApJ...888..113W} studied the properties of high-\(z\) and local \hii{} galaxies among some GEHRs finding a value of \(\alpha \sim 5\).

There are two main difference between the previous investigations and our results: one is that the velocity dispersion is obtained as the width of the emission line profile integrated over the whole object or as the non-thermal line-width, which is different from the plane of the sky dispersion we are using and that our sample is considerably smaller in the data points.
The first problem is addressed in section \ref{sec:sigmapos-vs-sigmalos} where we discuss the relation between the line-of-sight and plane-of-sky velocities.
But despite these problems, the fact that this relationship holds in our results (within the errors) is interesting considering that the \(\sigma\pos\) is derived from the structure function, while the \(\text{L}(\ha)\) values comes from different sources unrelated to our data (see the Appendix~\ref{sec:notes-individual-hii}).
This means that the proposed structure function model describes within certain accuracy the velocity field fluctuations and that the parameters obtained can be interpreted as a true kinematic property of the \hii{} region velocity field.

@@

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc} ; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}. 
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation with a large population of young star, some of which are the sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along its stellar population are documented in \citet{2001ARA&A..39...99O}.

@@

\

\textit{Orion core}

\
Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
Using the observed structure function and by simple linear interpolation the value of \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.05}{pc} \) (as comparison to the derived values from our model which are \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \) (this \(r\) value would be analog to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
The maximum \(B(r)\) value correspond to \SI{23}{km^{2}.s^{-2}} at \(r = \SI{0.30}{pc}\).
From this value the \(B(r)\) values decrease and it is possible to observe a downturn in the structure function from to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
This 'hook' behavior is described by the tapered fluctuations (see section~\ref{sec:limit-model-struct}).
If we consider the first valid point of \(B(r)\) to be above the derived value of \(s_0\), which corresponds to \SI{0.3}{km^{2}.s^{-2}} at \(r = \SI{0.003}{pc} \) and use a linear relation to calculate the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.66} and \num{0.89}, respectively, while our derived value is \num{1}.

\textit{EON}

@@

%The seeing width is much smaller than the angular scale of the observations

\subsubsection{Comparison with previous studies}
\label{sec:comparison-orion}

@@

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}.
These stars gives an ionizing flux \(Q_0\) of \SI{e49.41}{photons.s^{-1}} (2 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

@@

We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
This region presents a non-uniform behavior below the derived correlation length but still it is possible to see the characteristic ascending values of the structure function.
The value of the observed \(\sigma\pos^2 = \SI{8}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{1}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{7}{km^{2}.s^{-2}}\) and \(r_0 = \SI{1}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{2.5}{pc} \).
From this point the structure function shows a 'reversed hook' behavior, which mean that there is a decrease in \(B(r)\) values up until \(r_0 = \SI{4}{pc} \)) for a value of \SI{11}{km^{2}.s^{-2}}, which from this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.
This may be because our observations doesn't cover and outer correlation region (see sections~\ref{sec:D-vs-r0}) or an indication of some periodic behavior (see sections~\ref{sec:limit-model-struct}).
There aren't any points affected by the seeing (RMS) which has a value of \SI{0.01}{pc} (\(s_0\)=\SI{3.5}{\arcsecond}).
If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{0.55}{km^{2}.s^{-2}} at \(r = \SI{0.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.89} and \num{0.86}, respectively, while our derived value is \num{1.26}.

@@

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
It contains young clusters like Trumpler 14 and 16, and Collinder 228 from the Car OB1 association, one of the largest OB associations in the Galaxy.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$ Car.
The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
As the Lagoon nebula, the structure function of Carina also shows a non-uniform and a more disperse behavior below the correlation length.
The value of the observed \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.5}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.5}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{1.6}{pc} \).
Above this separation, at larges scales, the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
Also, it can be argue that at large scales the behavior does not reflect purely the homogeneous fluctuations. 
It seems that there are two  oscillating pattern at large scales.
The first one, from \(r = \SI{1.7}{pc} \) to \SI{6}{pc} which has an spatial wavelength of \SI{\sim 2}{pc} and a dispersion of \SI{1}{km^{2}.s^{-2}}.
The second one when \(r >\)\SI{6}{pc} until \SI{7}{pc} with a dispersion of \SI{3.5}{km^{2}.s^{-2}}.
This fluctuations are around the value of 2\(\sigma^2\pos\) so it is possible that the dispersion is artificial because of the multi-fiber observations (see section~\ref{sec:flames-multi-fiber}).
There aren't any points affected by the seeing (RMS) which has a value of \SI{0.015}{pc} (\(s_0\)=\SI{3.4}{\arcsecond}).
If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{4}{km^{2}.s^{-2}} at \(r = \SI{0.01}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.38} and \num{0.43}, respectively, while our derived value is \num{1.16}.

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive dense star cluster R136
with ionizing output \(Q_0\) of is \SI{e51.40}{photons.s^{-1}} \citep{2020MNRAS.499.1918B} and the luminosity in \ha{} of \SI{e39.46}{erg.s^{-1}} (194 times higher compared to the Orion Nebula).
%\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C} and host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

The first attempt at characterizing turbulence in a giant extragalactic \hii{} region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
\citet{Melnick:2021x} also investigated the structure function in 30~Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
This is the first time turbulence is characterized in 30~Doradus using the structure function.
